### 2022-03-02 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@943bf0a37a1706bd64fc5717e74f7377744217d6 🚀

\begin{figure}
\hypertarget{fig:ecovalid}{%
\centering
\includegraphics{figures/valid_ensemble.png}
\caption{Visualisation of the models predictions for one instance of a
network prediction problem (shown in the ``Dataset'' panel). This figure
reveals how inspecting the details of the prediction is important:
indeed, although the performance measures hint at the fact that ridge
regression is mediocre, this figure reveals that it is making
predictions that correspond to a network with an entirely different
topology (namely, nested as opposed to diagonal).}\label{fig:ecovalid}
}
\end{figure}

@@

\hypertarget{guidelines-for-the-assesment-of-network-predictive-models}{%
\section{Guidelines for the assesment of network predictive
models}\label{guidelines-for-the-assesment-of-network-predictive-models}}

@@

Finally, it is noteworthy that the ensemble model was systematically
better than the component models; even when the models were individually
far form perfect, the ensemble was able to leverage the different biases
expressed by the models to make an overall more accurate prediction. We
do not expect that ensembles will \emph{always} be better than single
models. In a recent multi-model comparison, (\textbf{Becker2022OptPre?})
found that the ensemble was \emph{not} the best model. There is no
general conclusion to draw from this besides reinforcing the need to be
pragmatic about which models should be included in the ensemble, or
whether to use an ensemble at all. In a sense, the surprising peformance
of the ensemble model should form the basis of the last recommendation:
optimal training set bias and its interaction with connectance and
binary classifier is, in a sense, an hyperparameter that should be
assessed. The distribution of results in fig.~\ref{fig:optimbias} and
fig.~\ref{fig:optimvalue} show that there are variations around the
trend; furthermore, networks with different structures than the one we
simulated here may respond in different ways.

>>>>

\begin{figure}
\hypertarget{fig:ecovalid}{%
\centering
\includegraphics{figures/valid_ensemble.png}
\caption{Visualisation of the raw (un-thresholded) models predictions
for one instance of a network prediction problem (shown in the
``Dataset'' panel). Increasing the value of the \(\xi\) parameter would
make the diagonal structure ``broader,'' leading to more interactions. A
visual inspection of the results is important, as it highlights how some
models can ``miss'' parts of the network; by combining them in an
ensemble, these gaps compensate one another, and lead (in this case) to
a better prediction.}\label{fig:ecovalid}
}
\end{figure}

@@

\hypertarget{guidelines-for-the-assessment-of-network-predictive-models}{%
\section{Guidelines for the assessment of network predictive
models}\label{guidelines-for-the-assessment-of-network-predictive-models}}

It is noteworthy that the ensemble model was systematically better than
the component models. We do not expect that ensembles will \emph{always}
be better than single models. Networks with different structures than
the one we simulated here may respond in different ways, especially if
the rules are fuzzier than the simple rule we used here. In a recent
multi-model comparison involving supervised and unsupervised learning,
(\textbf{Becker2022OptPre?}) found that the ensemble was \emph{not} the
best model. There is no general conclusion to draw from this besides
reinforcing the need to be pragmatic about which models should be
included in the ensemble, or whether to use an ensemble at all. In a
sense, the surprising performance of the ensemble model should form the
basis of the last recommendation: optimal training set balance and its
interaction with connectance and the specific binary classifier used is,
in a sense, an hyperparameter that should be assessed. The distribution
of results in fig.~\ref{fig:optimbias} and fig.~\ref{fig:optimvalue}
show that there are variations around the trend. TODO fix this sentence

(\textbf{Xie2017ComCom?}) - most networks have SBM structure ---
(\textbf{Valdovinos2019MutNet?}) matching + forbidden
(\textbf{Olesen2011MisFor?}), coming up with matching rules that
allow/forbid links can make predictions easier
(\textbf{Strona2017ForPer?}); but valid for most type of interactions as
long as we can match yes/no to numeric predictors

@@
